---
title: "Replicating #No2Sectarianism"

subtitle: 'Siegel, Alexandra A. and Vivienne Badaan. 2020. "#No2Sectarianism: Experimental Approaches to Reducing Sectarian Hate Speech Online." *American Journal of Political Science* 114:3, 837-855.'

date: "10 December 2020 | PS812 | UW-Madison"
author: "Jess Esplin, J. Clinton Rooker, and Ethan vanderWilden"


output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Setting and Question

- What kinds of interventions reduce sectarian online hate speech?


- Arab Twittersphere experiment & counter-speech interventions


- Identity recategorization & in-group norms

\newpage
## Data and Methods

- Original data collected from Twitter following counter-speech interventions with a "sock-puppet"


- 5 treatments, 1 control group
  - Elite Common Religious Identity
  - Elite Common National Identity
  - Common Religious Identity
  - Common National Identity
  - No prime; only the sanction
  - Control; no tweet reply/intervention


- Difference in means tests, confidence intervals

\newpage
## Hypotheses

- General Form: 
  - let $x$ =  pre-treatment sectarian tweets - post-treatment sectarian tweets

  - $H_0$: $\bar{x}_{treatment} - \bar{x}_{control} \geq 0$
  - $H_A$: $\bar{x}_{treatment} - \bar{x}_{control} < 0$

- Example of treatment hypothesis: "Receiving a response to a hateful sectarian message that primes a common Muslim religious identity and highlights support from religious leaders will make individuals less likely to tweet hateful sectarian messages in the future" (841)

\newpage
## Results

```{r,include=FALSE}

# packages
library("magrittr")
library("tidyverse")
library("haven")
library("here")
library("stargazer")
library("modelsummary")
library("sjlabelled")
library(coefplot)

# working directory
getwd()

#Load in Data
data <- read.csv("siegel-badaan_data/twitter_data.csv")

# We want the treatment variable as a 'factor' (for its data type)
# because we want to compare different treatments to the control situation
data$treat <- as.factor(data$treatment_num)

#getting post- and pre-treatment difference:
data$month_diff <- data$month_anti_shia_post - data$month_anti_shia_pre
data$twoweek_diff <- data$two_weeks_anti_shia_post - data$two_weeks_anti_shia_pre
data$week_diff <- data$week_anti_shia_post - data$week_anti_shia_pre
data$day_diff <- data$tpd_anti_shia_post - data$tpd_anti_shia_pre

### FOR MAIN FIGURE

#Run linear regression that is testing for difference in means of 
# certain treatment - control group
month<-lm(month_diff ~ treat, data=data)
two_weeks<-lm(twoweek_diff ~ treat, data=data)
week<-lm(week_diff ~ treat, data=data)
day<-lm(day_diff ~ treat, data=data)
```

```{r, include=F}
#Present results in table
stargazer(day, week, two_weeks, month,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "text",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets")
```

```{r, warning=F}
multiplot(day, week, two_weeks, month, coefficients=c("treat1", "treat2", "treat3", "treat4", "treat5"), 
          newNames=c(treat1="Arab ID ", treat2="Religious ID ", treat3="Arab ID (Elite)", 
                     treat4="Religious ID (Elite)", treat5=" No ID "), 
          names=c("     Day", "   Week", "  Two Weeks ", "Month    "), 
          title="Effect of Treatment on Volume of Anti-Shia Tweets, 90 and 95% CIs", scales="free_x",
          sort="alphabetical", innerCI=1.645, outerCI=1.96, single=FALSE,  zeroType = 0,legend.position="none") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.line = element_line(colour = "black"), text = element_text(size=15))+
  ylab("Treatments") + xlab("Difference in Anti-Shia Tweet Count")+ geom_vline(aes(xintercept = 0), size = .5, linetype = "dashed")

```

\newpage
## Conclusion and Steps Forward

- Support for elite-endorsed common religious identity prime hypothesis
  - Cannot reject the null for other treatments

- Results hold up to robustness checks

- Pathways Forward
  - Multiple interventions
  - Other social media platforms
  - Anti-Shia network saturation

\newpage
## Appendix: Tables and Robustness Checks

\begin{itemize}
\item[1)] Main Figure Regression Table
\item[2)] Median Follower Subset Figure
\item[3)] Median Follower Subset Regression Table
\item[4)] Low Anti-Shia Saturation Figure
\item[5)] Low Anti-Shia Saturation Regression Table
\item[6)] High Anti-Shia Saturation Figure
\item[7)] High Anti-Shia Saturation Regression Table
\end{itemize}

\newpage
## 1. Main Figure Regression Table

```{r, results='asis'}
#Present results in table
stargazer(day, week, two_weeks, month,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("Day", "Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "latex",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets",
          font.size = "tiny", header = FALSE, omit.stat=c("f", "ser"))
```


\newpage
## 2. Robustness (Less than Median Followers)

```{r , include = F}
### ROBUSTNESS CHECK - MEDIAN SUBSET

summary(data$followers_count) #see that median = 245
#subset the data to only look at accounts at or below the median follower count
data_median <- subset(data, data$followers_count<=245)

#Run linear regression that is testing for difference in means of 
# certain treatment - control group
month_med <-lm(month_diff ~ treat, data=data_median)
two_weeks_med <-lm(twoweek_diff ~ treat, data=data_median)
week_med <-lm(week_diff ~ treat, data=data_median)
day_med <-lm(day_diff ~ treat, data=data_median)

#Present results in table
stargazer(day_med, week_med, two_weeks_med, month_med,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "text",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Fewer Follower Subset)")
```

```{r}
multiplot(day_med, week_med, two_weeks_med, month_med, coefficients=c("treat1", "treat2", "treat3", "treat4", "treat5"), 
          newNames=c(treat1="Arab ID ", treat2="Religious ID ", treat3="Arab ID (Elite)", 
                     treat4="Religious ID (Elite)", treat5=" No ID "), 
          names=c("     Day", "   Week", "  Two Weeks ", "Month    "), 
          title="Effect of Treatment on Volume of Anti-Shia Tweets (Median or Fewer Follower Subset)", scales="free_x",
          sort="alphabetical", innerCI=1.645, outerCI=1.96, single=FALSE,  zeroType = 0,legend.position="none") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.line = element_line(colour = "black"), text = element_text(size=15))+
  ylab("Treatments") + xlab("Difference in Anti-Shia Tweet Count")+ geom_vline(aes(xintercept = 0), size = .5, linetype = "dashed")
```

\newpage
## 3. Regression Table, Median Robustness Check

```{r, results='asis'}
stargazer(day_med, week_med, two_weeks_med, month_med,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "latex",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Fewer Follower Subset)",
          font.size = "tiny", header = FALSE, omit.stat=c("f", "ser"))
```

\newpage
## 4. Robustness Checks (Network Saturation - Low)

```{r, include=F}
data$friends_prop <- (data$anti_shia_friends_count/data$followers_count)

#UNDERSATTURATED NETWORK

#It is possible that the intervention is stronger on those with extremely anti-Shia 
# saturated networks (ie, they follow many Anti-Shia people proportional to their 
# overall twitter presence)
not_saturated <- subset(data, data$friends_prop<=0.156024)

#Run linear regression that is testing for difference in means of 
# certain treatment - control group
month_NS <-lm(month_diff ~ treat, data=not_saturated)
two_weeks_NS <-lm(twoweek_diff ~ treat, data=not_saturated)
week_NS <-lm(week_diff ~ treat, data=not_saturated)
day_NS <-lm(day_diff ~ treat, data=not_saturated)

stargazer(day_NS, week_NS, two_weeks_NS, month_NS,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "text",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Less Saturnated Network Subset)")

#OVERSATURATED NETWORK

#It is possible that the intervention is stronger on those with extremely anti-Shia 
# saturated networks (ie, they follow many Anti-Shia people proportional to their 
# overall twitter presence)
saturated_network <- subset(data, data$friends_prop>=0.156024)

#Run linear regression that is testing for difference in means of 
# certain treatment - control group
month_satnet <-lm(month_diff ~ treat, data=saturated_network)
two_weeks_satnet <-lm(twoweek_diff ~ treat, data=saturated_network)
week_satnet <-lm(week_diff ~ treat, data=saturated_network)
day_satnet <-lm(day_diff ~ treat, data=saturated_network)

stargazer(day_satnet, week_satnet, two_weeks_satnet, month_satnet,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "text",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Greater Saturnated Network Subset)")

```


```{r}
multiplot(day_NS, week_NS, two_weeks_NS, month_NS, coefficients=c("treat1", "treat2", "treat3", "treat4", "treat5"), 
          newNames=c(treat1="Arab ID ", treat2="Religious ID ", treat3="Arab ID (Elite)", 
                     treat4="Religious ID (Elite)", treat5=" No ID "), 
          names=c("     Day", "   Week", "  Two Weeks ", "Month    "), 
          title="Effect of Treatment on Volume of Anti-Shia Tweets (Median or Less Saturnated Network Subset)", scales="free_x",
          sort="alphabetical", innerCI=1.645, outerCI=1.96, single=FALSE,  zeroType = 0,legend.position="none") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.line = element_line(colour = "black"), text = element_text(size=15))+
  ylab("Treatments") + xlab("Difference in Anti-Shia Tweet Count")+ geom_vline(aes(xintercept = 0), size = .5, linetype = "dashed")
```


\newpage
## 5. Regression Table, Low Anti-Shia Network Saturation
```{r, results='asis'}
stargazer(day_NS, week_NS, two_weeks_NS, month_NS,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "latex",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Less Saturnated Network Subset)",
          font.size = "tiny", header=FALSE, omit.stat=c("f", "ser"))
```


\newpage
## 6. Robustness Checks (Network Saturation - High)
```{r}
multiplot(day_satnet, week_satnet, two_weeks_satnet, month_satnet, coefficients=c("treat1", "treat2", "treat3", "treat4", "treat5"), 
          newNames=c(treat1="Arab ID ", treat2="Religious ID ", treat3="Arab ID (Elite)", 
                     treat4="Religious ID (Elite)", treat5=" No ID "), 
          names=c("     Day", "   Week", "  Two Weeks ", "Month    "), 
          title="Effect of Treatment on Volume of Anti-Shia Tweets (Median or Greater Saturnated Network Subset)", scales="free_x",
          sort="alphabetical", innerCI=1.645, outerCI=1.96, single=FALSE,  zeroType = 0,legend.position="none") +
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="none", axis.line = element_line(colour = "black"), text = element_text(size=15))+
  ylab("Treatments") + xlab("Difference in Anti-Shia Tweet Count")+ geom_vline(aes(xintercept = 0), size = .5, linetype = "dashed")
```


\newpage
## 7. Regression Table, High Anti-Shia Network Saturation
```{r, results='asis'}
stargazer(day_satnet, week_satnet, two_weeks_satnet, month_satnet,
          covariate.labels = c("Arab ID", "Religious ID",
                               "Arab ID (elite)", "Religious ID (elite)",
                               "No ID"),
          column.labels = c("One Day", "One Week", "Two Weeks", "One Month"),
          dep.var.caption = "Difference in Anti-Shiea Tweets",
          dep.var.labels.include = FALSE,
          type = "latex",
          title = "Effect of Treatment on Volume of Anti-Shia Tweets (Median or Greater Saturnated Network Subset)",
          font.size = "tiny", header=FALSE, omit.stat=c("f", "ser"))
```

